Towards a standardized evaluation of multiple imputation routines

### 2022-02-09 Manuscript/StandardizedEvaluation.Rmd
Before full sim

# gtsummary::tbl_summary(sim_nobs, by = dat)
# https://haozhu233.github.io/kableExtra/awesome_table_in_html.html#Group_rows_via_labeling
sim_nobs %>% 
  group_by(n_obs, dat) %>% 
  summarise(
    mean_Y = mean(ave),
    beta_X = mean(est),
    CIW = mean(ciw),
    CR = mean(cov),
    RMSE_pred = mean(rmse_pred),
    RMSE_cell = mean(rmse_cell, na.rm = TRUE))  %>% 
  .[, -1] %>% 
  knitr::kable(
    col.names = c("", "$\\mu_{Y} = 10$", "$\\beta_{X} = 0.4$", "CIW", "CR", "RMSE$_{p}$", "RMSE$_{c}$"), 
    digits = 3,
    escape = FALSE) %>% 
  kableExtra::kable_classic(full_width = TRUE) %>% 
  kableExtra::pack_rows(group_label = "$n = 50$", 1, 3) %>% 
  kableExtra::pack_rows(group_label = "$n = 500$", 4, 6) %>% 
  kableExtra::pack_rows(group_label = "$n = 5000$", 7, 9)

>>>>

# gtsummary::tbl_summary(sim_nobs, by = dat)
# https://haozhu233.github.io/kableExtra/awesome_table_in_html.html#Group_rows_via_labeling
sim_nobs %>% 
  group_by(n_obs, dat) %>% 
  summarise(
    mean_Y = mean(ave),
    beta_X = mean(est),
    CIW = mean(ciw),
    CR = mean(cov),
    RMSE_pred = mean(rmse_pred),
    RMSE_cell = mean(rmse_cell, na.rm = TRUE))  %>% 
  .[, -1] %>% 
  knitr::kable(
    col.names = c("", "$\\mu_{Y} = 10$", "$\\beta_{X} = 0.4$", "CIW", "CR", "RMSE$_{p}$", "RMSE$_{c}$"), 
    digits = 3,
    escape = FALSE) %>% 
  kableExtra::kable_classic(full_width = TRUE) %>% 
  kableExtra::pack_rows(group_label = "$n = 50$", 1, 3, escape = FALSE) %>% 
  kableExtra::pack_rows(group_label = "$n = 500$", 4, 6, escape = FALSE) %>% 
  kableExtra::pack_rows(group_label = "$n = 5000$", 7, 9, escape = FALSE)
